---
title: "CSCL2023"
author: "Yuanru"
date: "2022-10-31"
output:
  html_document:
    toc: yes
    df_print: paged
  html_notebook:
    toc: yes
editor_options: 
  markdown: 
    wrap: sentence
---

```{=html}
<style>
  table, th, td {border: 1px solid black; padding: 10px;background-color:#eeeeee}
  table.center {
  margin-left: auto;
  margin-right: auto;
}
</style>
```


```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

Ayano: we need to install tma package too to use ona package
```{r install ONA package}
#install.packages("ona", repos = c("https://epistemic-analytics.gitlab.io/qe-packages/ona/cran/", "https://cran.rstudio.org"))
#install.packages("tma", repos = c("https://epistemic-analytics.gitlab.io/qe-packages/tma/cran/", "https://cran.rstudio.org"))
```


```{r include=FALSE}
library(ona)
library(tma)
library(magrittr)
```

most recent data Ayano shared
```{r}
data <- read.csv("PES_010v4(Selection)_20221024.csv")
colnames(data)
```

update: Ayano suggested that we remove Product Designers lines from the data. nrow 1345 -> 910
```{r}
data = data[data$Role == "Engineer" | data$Role == "ServiceDesigner",]
```


```{r}
units <- c("Speaker", "Role", "TimePhase")

codes_1 <- c("Function", "Aesthetic", "User", "Vision", "Prototyping") # design actions codes
codes_2 <- c("CA", "ALoK", "CSU", "GCA", "Projective","Regulative","Relational") # shared epistemic agency codes

hoo_rules <- conversation_rules(
  (TimePhase %in% UNIT$TimePhase & Role %in% UNIT$Role)
)
```

notes for Ayano: accum_1 and set_1 are for design action codes; accum_2 and set_2 are for shared epistemic agency codes

```{r}
accum_1 <-
  contexts(data, 
           units_by = units, 
           hoo_rules = hoo_rules) %>%
  accumulate_contexts(codes = codes_1, 
                      decay.function = decay(simple_window, window_size = 4),
                      return.ena.set = FALSE, norm.by = NULL)
```


```{r}
set_1 <-
  model(accum_1,
        rotate.using = "mean",
        rotation.params = 
          list(engineers=accum_1$meta.data$Role=="Engineer",
               servicedesigners=accum_1$meta.data$Role=="ServiceDesigner"))
```


```{r}
accum_2 <-
  contexts(data, 
           units_by = units, 
           hoo_rules = hoo_rules) %>%
  accumulate_contexts(codes = codes_2, 
                      decay.function = decay(simple_window, window_size = 4),
                      return.ena.set = FALSE, norm.by = NULL)
```


```{r}
set_2 <-
  model(accum_2,
        rotate.using = "mean",
        rotation.params = 
          list(engineers=accum_2$meta.data$Role=="Engineer",
               servicedesigners=accum_2$meta.data$Role=="ServiceDesigner"))
```

you can save set so you don't have to run lines above next time
```{r}
saveRDS(set_1, "ayano_set_1_design_codes.RDS")
saveRDS(set_2, "ayano_set_2_epistemic_codes.RDS")
```


global visual parameter (let's make sure all the plots use the same level of multiplier)
```{r}
edge_arrow_saturation_multiplier = 1.5
edge_size_multiplier = 1
node_size_multiplier = 0.6
point_position_multiplier = 1
```


Model 1: design action codes
```{r}
TimePhase <- as.list(unique(data$TimePhase))

# individual networks
# for (i in TimePhase) {
  # print(i)
  # print(
  #   plot(set_1, title = paste0("Phase",i," Engineering team", "(design codes)")) %>%
  #     edges(
  #       weights = colMeans(set_1$line.weights[TimePhase == i & Role == 'Engineer' & ENA_DIRECTION == 'response']),
  #       edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier, edge_size_multiplier = edge_size_multiplier, edge_color = c("blue")) %>%
  #     units(
  #       points=set_1$points[TimePhase == i & Role == 'Engineer'], 
  #       points_color = "blue", point_position_multiplier = point_position_multiplier, 
  #       show_mean = FALSE, show_points = FALSE, with_ci = TRUE) %>%
  #     nodes(
  #       node_labels = FALSE,
  #       node_size_multiplier = node_size_multiplier,
  #       self_connection_color = c("blue"))
  # )
  # print(
  #   plot(set_1, title = paste0("Phase",i," Product design team", "(design codes)")) %>%
  #     edges(
  #       weights = colMeans(set_1$line.weights[TimePhase == i & Role == 'ProductDesigner' & ENA_DIRECTION == 'response']),
  #       edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier, edge_size_multiplier = edge_size_multiplier, edge_color = c("red")) %>%
  #     units(
  #       points=set_1$points[TimePhase == i & Role == 'ProductDesigner'], 
  #       points_color = "red", point_position_multiplier = point_position_multiplier, 
  #       show_mean = TRUE, show_points = TRUE, with_ci = TRUE) %>%
  #     nodes(self_connection_color = c("red"))
  # )
#   print(
#     plot(set_1, title = paste0("Phase",i," Service designer team", "(design codes)")) %>%
#       edges(
#         weights = colMeans(set_1$line.weights[TimePhase == i & Role == 'ServiceDesigner' & ENA_DIRECTION == 'response']),
#         edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier, edge_size_multiplier = edge_size_multiplier, edge_color = c("red")) %>%
#       units(
#         points=set_1$points[TimePhase == i & Role == 'ServiceDesigner'], 
#         points_color = "red", point_position_multiplier = point_position_multiplier, 
#         show_mean = FALSE, show_points = FALSE, with_ci = TRUE) %>%
#       nodes(
#         node_labels = FALSE,
#         node_size_multiplier = node_size_multiplier,
#         self_connection_color = c("red"))
#   )
# }

# subtracted networks 
for (i in TimePhase) {
#   print(i)
  # print(
  #   plot(set_1, title = paste0("Phase",i," Engineers(blue) vs ProductDesigners(red)", "(design codes)")) %>%
  #     edges(
  #       weights = colMeans(set_1$line.weights[TimePhase == i & Role == 'Engineer' & ENA_DIRECTION == 'response']) -
  #         colMeans(set_1$line.weights[TimePhase == i & Role == 'ProductDesigner' & ENA_DIRECTION == 'response']),
  #       edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier, edge_size_multiplier = edge_size_multiplier, 
  #       edge_color = c("blue", "red")) %>%
  #     units(
  #       points=set_1$points[TimePhase == i & Role == 'Engineer'], 
  #       points_color = "blue", point_position_multiplier = point_position_multiplier, 
  #       show_mean = TRUE, show_points = TRUE, with_ci = TRUE) %>%
  #     units(
  #       points=set_1$points[TimePhase == i & Role == 'ProductDesigner'], 
  #       points_color = "red", point_position_multiplier = point_position_multiplier, 
  #       show_mean = TRUE, show_points = TRUE, with_ci = TRUE) %>%
  #     nodes(self_connection_color = c("blue", "red"))
  # )
  # 
  print(
    plot(set_1, title = paste0("Phase",i," Engineers(blue) vs ServiceDesigners(red)", "(design codes)")) %>%
      edges(
        weights = (colMeans(set_1$line.weights[TimePhase == i & Role == 'Engineer' & ENA_DIRECTION == 'response']) -
          colMeans(set_1$line.weights[TimePhase == i & Role == 'ServiceDesigner' & ENA_DIRECTION == 'response'])),
        edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier, edge_size_multiplier = edge_size_multiplier,
        edge_color = c("blue", "red")) %>%
      units(
        points=set_1$points[TimePhase == i & Role == 'Engineer'],
        points_color = "blue", point_position_multiplier = point_position_multiplier,
        show_mean = FALSE, show_points = FALSE, with_ci = TRUE) %>%
      units(
        points=set_1$points[TimePhase == i & Role == 'ServiceDesigner'],
        points_color = "red", point_position_multiplier = point_position_multiplier,
        show_mean = FALSE, show_points = FALSE, with_ci = TRUE) %>%
      nodes(
        node_labels = FALSE,
        node_size_multiplier = node_size_multiplier,
        self_connection_color = c("blue", "red"))
  )
  
  # print(
  #   plot(set_1, title = paste0("Phase",i," ProductDesigners(red) vs ServiceDesigners(green)", "(design codes)")) %>%
  #     edges(
  #       weights = colMeans(set_1$line.weights[TimePhase == i & Role == 'ProductDesigner' & ENA_DIRECTION == 'response']) -
  #         colMeans(set_1$line.weights[TimePhase == i & Role == 'ServiceDesigner' & ENA_DIRECTION == 'response']),
  #       edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier, edge_size_multiplier = edge_size_multiplier, 
  #       edge_color = c("red", "green")) %>%
  #     units(
  #       points=set_1$points[TimePhase == i & Role == 'ProductDesigner'], 
  #       points_color = "red", point_position_multiplier = point_position_multiplier, 
  #       show_mean = TRUE, show_points = TRUE, with_ci = TRUE) %>%
  #     units(
  #       points=set_1$points[TimePhase == i & Role == 'ServiceDesigner'], 
  #       points_color = "green", point_position_multiplier = point_position_multiplier, 
  #       show_mean = TRUE, show_points = TRUE, with_ci = TRUE) %>%
  #     nodes(self_connection_color = c("red", "green"))
  # )
}
```

Model 2: shared epistemic agency codes
```{r}
TimePhase <- as.list(unique(data$TimePhase))

# individual networks
# for (i in TimePhase) {
#   print(i)
#   print(
#     plot(set_2, title = paste0("Phase",i," Engineering team", "(epistemic codes)")) %>%
#       edges(
#         weights = colMeans(set_2$line.weights[TimePhase == i & Role == 'Engineer' & ENA_DIRECTION == 'response']),
#         edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier, edge_size_multiplier = edge_size_multiplier, edge_color = c("blue")) %>%
#       units(
#         points=set_2$points[TimePhase == i & Role == 'Engineer'], 
#         points_color = "blue", point_position_multiplier = point_position_multiplier, 
#         show_mean = FALSE, show_points = FALSE, with_ci = TRUE) %>%
#       nodes(
#         node_labels = FALSE,
#         node_size_multiplier = node_size_multiplier,
#         self_connection_color = c("blue"))
#   )
  # print(
  #   plot(set_2, title = paste0("Phase",i," Product design team", "(epistemic codes)")) %>%
  #     edges(
  #       weights = colMeans(set_2$line.weights[TimePhase == i & Role == 'ProductDesigner' & ENA_DIRECTION == 'response']),
  #       edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier, edge_size_multiplier = edge_size_multiplier, edge_color = c("red")) %>%
  #     units(
  #       points=set_2$points[TimePhase == i & Role == 'ProductDesigner'], 
  #       points_color = "red", point_position_multiplier = point_position_multiplier, 
  #       show_mean = TRUE, show_points = TRUE, with_ci = TRUE) %>%
  #     nodes(self_connection_color = c("red"))
  # )
#   print(
#     plot(set_2, title = paste0("Phase",i," Service designer team", "(epistemic codes)")) %>%
#       edges(
#         weights = colMeans(set_2$line.weights[TimePhase == i & Role == 'ServiceDesigner' & ENA_DIRECTION == 'response']),
#         edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier, edge_size_multiplier = edge_size_multiplier, edge_color = c("red")) %>%
#       units(
#         points=set_2$points[TimePhase == i & Role == 'ServiceDesigner'], 
#         points_color = "red", point_position_multiplier = point_position_multiplier, 
#         show_mean = FALSE, show_points = FALSE, with_ci = TRUE) %>%
#       nodes(
#         node_labels = FALSE,
#         node_size_multiplier = node_size_multiplier,
#         self_connection_color = c("red"))
#   )
# }

# subtracted networks 
for (i in TimePhase) {
#   print(i)
  # print(
  #   plot(set_2, title = paste0("Phase",i," Engineers(blue) vs ProductDesigners(red)", "(epistemic codes)")) %>%
  #     edges(
  #       weights = colMeans(set_2$line.weights[TimePhase == i & Role == 'Engineer' & ENA_DIRECTION == 'response']) -
  #         colMeans(set_2$line.weights[TimePhase == i & Role == 'ProductDesigner' & ENA_DIRECTION == 'response']),
  #       edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier, edge_size_multiplier = edge_size_multiplier, 
  #       edge_color = c("blue", "red")) %>%
  #     units(
  #       points=set_2$points[TimePhase == i & Role == 'Engineer'], 
  #       points_color = "blue", point_position_multiplier = point_position_multiplier, 
  #       show_mean = TRUE, show_points = TRUE, with_ci = TRUE) %>%
  #     units(
  #       points=set_2$points[TimePhase == i & Role == 'ProductDesigner'], 
  #       points_color = "red", point_position_multiplier = point_position_multiplier, 
  #       show_mean = TRUE, show_points = TRUE, with_ci = TRUE) %>%
  #     nodes(self_connection_color = c("blue", "red"))
  # )
  
  print(
    plot(set_2, title = paste0("Phase",i," Engineers(blue) vs ServiceDesigners(green)", "(epistemic codes)")) %>%
      edges(
        weights = colMeans(set_2$line.weights[TimePhase == i & Role == 'Engineer' & ENA_DIRECTION == 'response']) -
          colMeans(set_2$line.weights[TimePhase == i & Role == 'ServiceDesigner' & ENA_DIRECTION == 'response']),
        edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier, edge_size_multiplier = edge_size_multiplier,
        edge_color = c("blue", "red")) %>%
      units(
        points=set_2$points[TimePhase == i & Role == 'Engineer'],
        points_color = "blue", point_position_multiplier = point_position_multiplier,
        show_mean = FALSE, show_points = FALSE, with_ci = TRUE) %>%
      units(
        points=set_2$points[TimePhase == i & Role == 'ServiceDesigner'],
        points_color = "red", point_position_multiplier = point_position_multiplier,
        show_mean = FALSE, show_points = FALSE, with_ci = TRUE) %>%
      nodes(
        node_labels = FALSE,
        node_size_multiplier = node_size_multiplier,
        self_connection_color = c("blue", "red"))
  )
#   
#   print(
#     plot(set_2, title = paste0("Phase",i," ProductDesigners(red) vs ServiceDesigners(green)", "(epistemic codes)")) %>%
#       edges(
#         weights = colMeans(set_2$line.weights[TimePhase == i & Role == 'ProductDesigner' & ENA_DIRECTION == 'response']) -
#           colMeans(set_2$line.weights[TimePhase == i & Role == 'ServiceDesigner' & ENA_DIRECTION == 'response']),
#         edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier, edge_size_multiplier = edge_size_multiplier,
#         edge_color = c("red", "green")) %>%
#       units(
#         points=set_2$points[TimePhase == i & Role == 'ProductDesigner'],
#         points_color = "red", point_position_multiplier = point_position_multiplier,
#         show_mean = TRUE, show_points = TRUE, with_ci = TRUE) %>%
#       units(
#         points=set_2$points[TimePhase == i & Role == 'ServiceDesigner'],
#         points_color = "green", point_position_multiplier = point_position_multiplier,
#         show_mean = TRUE, show_points = TRUE, with_ci = TRUE) %>%
#       nodes(self_connection_color = c("red", "green"))
#   )
}
```


group comparison 
```{r}
# design code model
eng = set_1$points[Role == 'Engineer'] 
eng_response_points <- eng[seq_len(nrow(eng)) %% 2 == 0, ]

# prod = set_1$points[Role == 'ProductDesigner'] 
# prod_response_points <- prod[seq_len(nrow(prod)) %% 2 == 0, ]

serv = set_1$points[Role == 'ServiceDesigner'] 
serv_response_points <- serv[seq_len(nrow(serv)) %% 2 == 0, ]

eng_points_d1 = as.matrix(eng_response_points)[,1]
# prod_points_d1 = as.matrix(prod_response_points)[,1]
serv_points_d1 = as.matrix(serv_response_points)[,1]

eng_points_d2 = as.matrix(eng_response_points)[,2]
# prod_points_d2 = as.matrix(prod_response_points)[,2]
serv_points_d2 = as.matrix(serv_response_points)[,2]


# test_d1_eng_prod = wilcox.test(eng_points_d1, prod_points_d1)
test_d1_eng_serv = wilcox.test(eng_points_d1, serv_points_d1)
# test_d1_prod_serv = wilcox.test(prod_points_d1, serv_points_d1)

# test_d2_eng_prod = wilcox.test(eng_points_d2, prod_points_d2)
test_d2_eng_serv = wilcox.test(eng_points_d2, serv_points_d2)
# test_d2_prod_serv = wilcox.test(prod_points_d2, serv_points_d2)

# test_d1_eng_prod 
test_d1_eng_serv 
# test_d1_prod_serv

# test_d2_eng_prod
test_d2_eng_serv
# test_d2_prod_serv

# esptemic code model
eng = set_2$points[Role == 'Engineer'] 
eng_response_points <- eng[seq_len(nrow(eng)) %% 2 == 0, ]

# prod = set_2$points[Role == 'ProductDesigner'] 
# prod_response_points <- prod[seq_len(nrow(prod)) %% 2 == 0, ]

serv = set_2$points[Role == 'ServiceDesigner'] 
serv_response_points <- serv[seq_len(nrow(serv)) %% 2 == 0, ]

eng_points_d1 = as.matrix(eng_response_points)[,1]
# prod_points_d1 = as.matrix(prod_response_points)[,1]
serv_points_d1 = as.matrix(serv_response_points)[,1]

eng_points_d2 = as.matrix(eng_response_points)[,2]
# prod_points_d2 = as.matrix(prod_response_points)[,2]
serv_points_d2 = as.matrix(serv_response_points)[,2]


# test_d1_eng_prod = wilcox.test(eng_points_d1, prod_points_d1)
test_d1_eng_serv = wilcox.test(eng_points_d1, serv_points_d1)
# test_d1_prod_serv = wilcox.test(prod_points_d1, serv_points_d1)

# test_d2_eng_prod = wilcox.test(eng_points_d2, prod_points_d2)
test_d2_eng_serv = wilcox.test(eng_points_d2, serv_points_d2)
# test_d2_prod_serv = wilcox.test(prod_points_d2, serv_points_d2)

# test_d1_eng_prod 
test_d1_eng_serv 
# test_d1_prod_serv

# test_d2_eng_prod
test_d2_eng_serv
# test_d2_prod_serv
```


