---
title: "JLA-ONA-2023"
author: "Zach & Yuanru"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: yes
  html_notebook:
    toc: yes
  html_document:
    toc: yes
    df_print: paged
editor_options:
  markdown:
    wrap: sentence
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list = ls())
```

```{r}
#install.packages("ona", repos = c("https://cran.qe-libs.org", "https://cran.rstudio.org")) # only run once
#install.packages("tma", repos = c("https://cran.qe-libs.org", "https://cran.rstudio.org")) # only run once
```

```{r include=FALSE}
library(ona)
library(tma)
library(magrittr)
library(tidyverse)
library(emmeans)
library(performance)
```

most recent data Ayano shared
```{r}
data <- read.csv("~/Rprojects/ayano/PES_010v6(selected).csv")
```

```{r}
units <- c("Speaker", "Role", "TimePhase")

codes_1 <- c("Functions", "Aesthetics", "User", "Vision", "Prototyping") # design actions codes
codes_2 <- c("CA", "ALoK", "CSU", "GCA", "Projective","Regulative","Relational") # shared epistemic agency codes

hoo_rules <- conversation_rules(
  (TimePhase %in% UNIT$TimePhase & Role %in% UNIT$Role)
)
```

notes: accum_1 and set_1 are for design action codes; accum_2 and set_2 are for shared epistemic agency codes

```{r}
accum_1 <-
  contexts(data, 
           units_by = units, 
           hoo_rules = hoo_rules) %>%
  accumulate_contexts(codes = codes_1, 
                      decay.function = decay(simple_window, window_size = 4),
                      return.ena.set = FALSE, norm.by = NULL)
```

Note: Not doing means rotation so I can compare everything in the same space

```{r}
set_1 <-
  # model(accum_1,
  #       rotate.using = "mean",
  #       rotation.params = 
  #         list(engineers=accum_1$meta.data$Role=="Engineer",
  #              servicedesigners=accum_1$meta.data$Role=="ServiceDesigner"))
  
  model(accum_1)
```

```{r}
accum_2 <-
  contexts(data, 
           units_by = units, 
           hoo_rules = hoo_rules) %>%
  accumulate_contexts(codes = codes_2, 
                      decay.function = decay(simple_window, window_size = 4),
                      return.ena.set = FALSE, norm.by = NULL)
```

```{r}
set_2 <-
  # model(accum_2,
  #       rotate.using = "mean",
  #       rotation.params = 
  #         list(engineers=accum_2$meta.data$Role=="Engineer",
  #              servicedesigners=accum_2$meta.data$Role=="ServiceDesigner"))
  
  model(accum_2)
```

global visual parameter (let's make sure all the plots use the same level of multiplier)
```{r}
node_size_multiplier = 0.3 # scale up or down node sizes
node_position_multiplier = 1 # zoom in or out node positions
point_position_multiplier = 1 # zoom in or out the point positions
edge_arrow_saturation_multiplier = 1.5 # adjust the chevron color lighter or darker
edge_size_multiplier = 1 # scale up or down edge sizes
```

Model 1: design action codes

Plot 1a: Overall Group Comparisons
```{r}
traces = c(2:10)
plot(set_1, title = "Groups") |>
  units(
    points= set_1$points$Role$ProductDesigner, 
    point_position_multiplier = point_position_multiplier,
    points_color = c("red"),
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
   units(
    points= set_1$points$Role$Engineer, 
    point_position_multiplier = point_position_multiplier,
    points_color = c("blue"),
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
   units(
    points= set_1$points$Role$ServiceDesigner, 
    point_position_multiplier = point_position_multiplier,
    points_color = c("green"),
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
  nodes(node_size_multiplier = 0.3,
            node_position_multiplier = node_position_multiplier,
            self_connection_color = c("black"))|>
      plotly::layout(showlegend = TRUE, legend = list(x = 100, y = 0.9)) |>
      plotly::style(name = "Product Designer", traces = traces[1]) |>
      plotly::style(name = "Engineer", traces = traces[2]) |>
      plotly::style(name = "Service Designer", traces = traces[3])
  
```
Plot 1b: Group subtractions
```{r}
prod_pts = set_1$points$Role$ProductDesigner 
eng_pts = set_1$points$Role$Engineer
serv_pts = set_1$points$Role$ServiceDesigner

prod_mean_net = set_1$line.weights %>% dplyr::filter(Role == "ProductDesigner") %>% colMeans()
eng_mean_net = set_1$line.weights %>% dplyr::filter(Role == "Engineer") %>% colMeans()
serv_mean_net = set_1$line.weights %>% dplyr::filter(Role == "ServiceDesigner") %>% colMeans()

plot(set_1, title = "Product Designer vs Engineer") |>
  units(
    points = prod_pts, 
    points_color = "red",
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
  units(
    points = eng_pts, 
    points_color = "blue",
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
  edges(
    weights = prod_mean_net - eng_mean_net, # optional multiplier to adjust for readability
    edge_size_multiplier = edge_size_multiplier,
    edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier,
    node_position_multiplier = node_position_multiplier,
    edge_color = c("red","blue")) |>
  nodes(
    node_size_multiplier = node_size_multiplier,
    node_position_multiplier = node_position_multiplier,
    self_connection_color = c("red","blue"))

plot(set_1, title = "Product Designer vs ServiceDesigner") |>
  units(
    points = prod_pts, 
    points_color = "red",
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
  units(
    points =serv_pts, 
    points_color = "green",
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
  edges(
    weights = prod_mean_net - serv_mean_net, # optional multiplier to adjust for readability
    edge_size_multiplier = edge_size_multiplier,
    edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier,
    node_position_multiplier = node_position_multiplier,
    edge_color = c("red","green")) |>
  nodes(
    node_size_multiplier = node_size_multiplier,
    node_position_multiplier = node_position_multiplier,
    self_connection_color = c("red","green"))

plot(set_1, title = "Service Designer vs Engineer") |>
  units(
    points = serv_pts, 
    points_color = "green",
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
  units(
    points = eng_pts, 
    points_color = "blue",
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
  edges(
    weights = serv_mean_net - eng_mean_net, # optional multiplier to adjust for readability
    edge_size_multiplier = edge_size_multiplier,
    edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier,
    node_position_multiplier = node_position_multiplier,
    edge_color = c("green","blue")) |>
  nodes(
    node_size_multiplier = node_size_multiplier,
    node_position_multiplier = node_position_multiplier,
    self_connection_color = c("green","blue"))
```
Plot 2: All Means by phase
```{r}

#get list of time phases and groups loop over or use map function

phases = unique(set_1$points$TimePhase)

groups = unique(set_1$points$Role)

col_list_2 = c("red",#phase 1
              "blue", #phase 2
              "green") #phase 3

traces = c(2:10)

x = plot(set_1, title = "Group Means by Phase")
count = 1
for (i in 1:length(phases)){
  for (j in 1:length(groups)){
    points = set_1$points %>% filter(TimePhase == phases[i], Role == groups[j])
    x = x |>
      units(
        points = points,
        point_position_multiplier = point_position_multiplier,
        points_color = col_list_2[i],
        show_mean = TRUE, show_points = F, with_ci = FALSE
        ) |>
      nodes(node_size_multiplier = 0.3,
            node_position_multiplier = node_position_multiplier,
            self_connection_color = c("black"))|>
      plotly::layout(showlegend = TRUE, legend = list(x = 100, y = 0.9)) |>
      plotly::style(name = paste0(phases[i]," - ",groups[j]), traces = traces[count])
    count = count + 1
  }
}

x

```

Statistical Tests:

In these data, the observations are nested within participants, so we need to check if this nesting 
has a significant effect. We do this by constructing a confidence interval
around the intraclass correlation coefficient (https://en.wikipedia.org/wiki/Intraclass_correlation). If the interval contains zero, nesting is not significant.

```{r}
reg_dat = set_1$points %>% filter(ENA_DIRECTION == "response")

ICC::ICCest(Speaker,SVD1,reg_dat) #not significant

ICC::ICCest(Speaker,SVD2,reg_dat) #not significant


```

Nesting is not significant so we proceed with an OLS regression. Below we set up two models for each dimension and test whether including interaction effects in the analysis significantly improves the modes.

```{r}
mod_x = lm(SVD1 ~ as.factor(TimePhase) + Role, data = reg_dat)
mod_y = lm(SVD2 ~ as.factor(TimePhase) + Role, data = reg_dat)

mod_x_2 = lm(SVD1 ~ as.factor(TimePhase)*Role, data = reg_dat)
anova(mod_x,mod_x_2)

mod_y_2 = lm(SVD2 ~ as.factor(TimePhase)*Role, data = reg_dat)
anova(mod_y,mod_y_2)

```
Interactions are significant, so we should use the interaction models. Let's view those models

```{r}
summary(mod_x_2)
summary(mod_y_2)
```
Viewing interactions
```{r}
emmip(mod_x_2, Role ~ TimePhase)
emmip(mod_y_2, Role ~ TimePhase)
```
When interactions are introduced, interpreting regression coefficients becomes more 
difficult, so we calculated the marginal means and various contrasts (i.e., comparisons between groups of interest) to address our research questions.

RQ1 (X dimension - Design Actions): Here we want to compare the "main effect" of Role on the x dimension---i.e., are there differences between the roles on the X dimension when averaging over TimePhases.

```{r}
emm_x1 = emmeans(mod_x_2, specs = pairwise ~ Role, weights = "proportional")
print(emm_x1$contrasts)
```
Only significant difference on the X is between Engineer and Service designer. Let's calculate the effect size (difference in standard deviations) of that difference. We will use Cohen's d.

```{r}
cohensd = function(diff_,g1,g2){
  diff_/(sqrt((sd(g1)^2 + sd(g2)^2)/2))
}

contrasts = as_tibble(emm_x1$contrasts)
diff_ = contrasts$estimate[2]
g1 = reg_dat %>% filter(Role == "Engineer") %>% select(SVD1)
g2 = reg_dat %>% filter(Role == "ServiceDesigner") %>% select(SVD1)

cohensd(diff_ = diff_,g1 = g1$SVD1,g2 = g2$SVD1)

```

RQ1 (Y dimension - Design Actions): Here we want to compare the "main effect" of Role on the y dimension---i.e., are there differences between the roles on the X dimension when averaging over TimePhases.

```{r}
emm_y1 = emmeans(mod_y_2, specs = pairwise ~ Role, weights = "proportional")
print(emm_y1$contrasts)
```
Significant differences between engineer/product designer and productdesigner/servicedesigner. Let's get the effect sizes:

```{r}
contrasts = as_tibble(emm_y1$contrasts)

diff_evp = contrasts$estimate[1]
g1 = reg_dat %>% filter(Role == "Engineer") %>% select(SVD1)
g2 = reg_dat %>% filter(Role == "ProductDesigner") %>% select(SVD1)

d_evp = cohensd(diff_ = diff_,g1 = g1$SVD1,g2 = g2$SVD1)

diff_pvs = contrasts$estimate[3]
g1 = reg_dat %>% filter(Role == "ProductDesigner") %>% select(SVD1)
g2 = reg_dat %>% filter(Role == "ServiceDesigner") %>% select(SVD1)

d_pvs = cohensd(diff_ = diff_,g1 = g1$SVD1,g2 = g2$SVD1)

d_evp
d_pvs
```

Marginal means - x RQ2


Here we use marginal means to test for differences between timephases within groups and groups within timephase and 

```{r}
library(emmeans)

emm_x1a = emmeans(mod_x_2, specs = pairwise ~ TimePhase|Role, weights = "proportional") #timephases w/n groups
emm_x1a = as_tibble(emm_x1a$contrasts)

emm_x2 = emmeans(mod_x_2, specs = pairwise ~ Role|TimePhase, weights = "proportional") #groups w/n timephases
emm_x2 = as_tibble(emm_x2$contrasts)

#see here: https://cran.r-project.org/web/packages/emmeans/vignettes/interactions.html

emm_x1a = emm_x1a %>% filter(p.value < 0.05)
emm_x2 = emm_x2 %>% filter(p.value < 0.05)

emm_x1a
emm_x2

```
Several contrasts are significant. Let's calculate the effect sizes
```{r}
cohensd_2 = function(diff_, sd1, sd2){
  cd = diff_/(sqrt((sd1^2 + sd2^2)/2))
  #print(sqrt((sd1^2 + sd2^2)/2))
  #print(diff_)
  return(cd)
}


sds.x = reg_dat %>% group_by(Role, as.factor(TimePhase)) %>% summarise(stdev = sd(SVD1))

#timephases w/n groups
eng_t1t2 = cohensd_2(emm_x1a$estimate[1],sd1 = sds.x$stdev[1], sd2 = sds.x$stdev[2]) ###FIX
eng_t1t3 = cohensd_2(emm_x1a$estimate[2],sd1 = sds.x$stdev[1], sd2 = sds.x$stdev[3])
pd_t1t2 = cohensd_2(emm_x1a$estimate[3],sd1 = sds.x$stdev[4], sd2 = sds.x$stdev[5])
pd_t1t3 = cohensd_2(emm_x1a$estimate[4],sd1 = sds.x$stdev[4], sd2 = sds.x$stdev[6])
sd_t1t3 = cohensd_2(emm_x1a$estimate[5],sd1 = sds.x$stdev[7], sd2 = sds.x$stdev[9])
sd_t2t3 = cohensd_2(emm_x1a$estimate[6],sd1 = sds.x$stdev[8], sd2 = sds.x$stdev[9])

print(list(eng_t1t2,eng_t1t3,pd_t1t2,pd_t1t3,sd_t1t3,sd_t2t3)) 


#groups w/n timephas
t1_evp = cohensd_2(emm_x2$estimate[1], sd1 = sds.x$stdev[1],sd2 = sds.x$stdev[4])
t1_evs = cohensd_2(emm_x2$estimate[2], sd1 = sds.x$stdev[1],sd2 = sds.x$stdev[7])
t2_evs = cohensd_2(emm_x2$estimate[3], sd1 = sds.x$stdev[2],sd2 = sds.x$stdev[8])
t2_pvs = cohensd_2(emm_x2$estimate[4], sd1 = sds.x$stdev[5],sd2 = sds.x$stdev[8])

print(list(t1_evp,t1_evs,t2_evs,t2_pvs))

```
Some of these are too large to be trusted. This is happening because some individuals are highly similar in the data. We will have to acknowledge this as it is likely due to small sample size


Marginal means -Y RQ2: Let's repeate what we did for X here
```{r}
emm_y1 = emmeans(mod_y_2, specs = pairwise ~ TimePhase|Role, weights = "proportional")
emm_y1 = as_tibble(emm_y1$contrasts)

emm_y2 = emmeans(mod_y_2, specs = pairwise ~ Role|TimePhase, weights = "proportional")
emm_y2 = as_tibble(emm_y2$contrasts)

emm_y1 = emm_y1 %>% filter(p.value < 0.05)
emm_y2 = emm_y2 %>% filter(p.value < 0.05)

emm_y1
emm_y2
```
Several contrasts are significant. Let's calculate the effect sizes

```{r}
sds.y = reg_dat %>% group_by(Role, as.factor(TimePhase)) %>% summarise(stdev = sd(SVD2))

#timephases w/n groups
eng_t1t3_y = cohensd_2(emm_y1$estimate[1],sd1 = sds.y$stdev[1], sd2 = sds.y$stdev[3])
eng_t2t3_y = cohensd_2(emm_y1$estimate[2],sd1 = sds.y$stdev[2], sd2 = sds.y$stdev[3])
pd_t1t3_y = cohensd_2(emm_y1$estimate[3],sd1 = sds.y$stdev[4], sd2 = sds.y$stdev[6])
pd_t2t3_y = cohensd_2(emm_y1$estimate[4],sd1 = sds.y$stdev[5], sd2 = sds.y$stdev[6])
sd_t1t2_y = cohensd_2(emm_y1$estimate[5],sd1 = sds.y$stdev[7], sd2 = sds.y$stdev[8])
sd_t1t3_y = cohensd_2(emm_y1$estimate[6],sd1 = sds.y$stdev[7], sd2 = sds.y$stdev[9])

print(list(eng_t1t3_y,eng_t2t3_y,pd_t1t3_y,pd_t2t3_y,sd_t1t2_y,sd_t1t3_y)) 


#groups w/n timephase
t1_ep_y = cohensd_2(emm_y2$estimate[1],sd1 = sds.y$stdev[1], sd2 = sds.y$stdev[4])
t1_es_y = cohensd_2(emm_y2$estimate[2],sd1 = sds.y$stdev[1], sd2 = sds.y$stdev[7])
t2_ep_y = cohensd_2(emm_y2$estimate[3],sd1 = sds.y$stdev[2], sd2 = sds.y$stdev[5])
t2_ps_y = cohensd_2(emm_y2$estimate[4],sd1 = sds.y$stdev[5], sd2 = sds.y$stdev[8])
t3_es_y = cohensd_2(emm_y2$estimate[5],sd1 = sds.y$stdev[3], sd2 = sds.y$stdev[9])
t3_ps_y = cohensd_2(emm_y2$estimate[6],sd1 = sds.y$stdev[6], sd2 = sds.y$stdev[9])

print(list(t1_ep_y,t1_es_y,t2_ep_y,t2_ps_y,t3_es_y,t3_ps_y))
```
Model diagnostics
```{r}
library(performance)
library(see)

check_model(mod_x_2)
check_model(mod_y_2)
```
Things look ok for the most part

Plot network subtractions (replace TimePhase and Role for different combinations)
```{r}
mean1 = set_1$points %>% dplyr::filter(TimePhase == 1, Role == "Engineer") #update here
mean2 = set_1$points %>% dplyr::filter(TimePhase == 1, Role == "ServiceDesigner") #update here

mean1_net = set_1$line.weights %>% dplyr::filter(TimePhase == 1, Role == "Engineer") %>% colMeans()
mean2_net = set_1$line.weights %>% dplyr::filter(TimePhase == 1, Role == "ServiceDesigner") %>% colMeans() #update here

plot(set_1, title = "Network subtraction") |>
  units(
    points = mean1, 
    points_color = "red",
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
  units(
    points = mean2, 
    points_color = "blue",
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
  edges(
    weights = mean1_net - mean2_net, # optional multiplier to adjust for readability
    edge_size_multiplier = edge_size_multiplier,
    edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier,
    node_position_multiplier = node_position_multiplier,
    edge_color = c("red","blue")) |>
  nodes(
    node_size_multiplier = node_size_multiplier,
    node_position_multiplier = node_position_multiplier,
    self_connection_color = c("red","blue"))


```

Model 2: Epistemic Agency Codes

Plot 1: Mean Network

```{r}
node_size_multiplier = 0.3 # scale up or down node sizes
node_position_multiplier = 1 # zoom in or out node positions
point_position_multiplier = 1 # zoom in or out the point positions
edge_arrow_saturation_multiplier = 1.5 # adjust the chevron color lighter or darker
edge_size_multiplier = 2 # scale up or down edge sizes
```


```{r}
plot(set_2, title = "Overall Mean--Agency") |>
  units(
    points= set_2$points, 
    point_position_multiplier = point_position_multiplier,
    points_color = c("black"),
    show_mean = TRUE, show_points = TRUE, with_ci = TRUE) |>
  edges(
    weights =set_2$line.weights,
    edge_size_multiplier = edge_size_multiplier,
    edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier,
    node_position_multiplier = node_position_multiplier,
    edge_color = c("black")) |>
  nodes(
    node_size_multiplier = node_size_multiplier,
    node_position_multiplier = node_position_multiplier,
    node_labels = TRUE, # change this to FALSE can remove node labels in case you want to add them back in a nicer font or size for your presentations or publications
    self_connection_color = c("black"))
```

Plot 1b: Overall Group Comparisons
```{r}
plot(set_2, title = "Groups") |>
  units(
    points= set_2$points$Role$ProductDesigner, 
    point_position_multiplier = point_position_multiplier,
    points_color = c("red"),
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
   units(
    points= set_2$points$Role$Engineer, 
    point_position_multiplier = point_position_multiplier,
    points_color = c("blue"),
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
   units(
    points= set_2$points$Role$ServiceDesigner, 
    point_position_multiplier = point_position_multiplier,
    points_color = c("green"),
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
  nodes(node_size_multiplier = 0.3,
            node_position_multiplier = node_position_multiplier,
            self_connection_color = c("black"))|>
      plotly::layout(showlegend = TRUE, legend = list(x = 100, y = 0.9)) |>
      plotly::style(name = "Product Designer", traces = traces[1]) |>
      plotly::style(name = "Engineer", traces = traces[2]) |>
      plotly::style(name = "Service Designer", traces = traces[3])
  
```
Plot 1c: Group subtractions
```{r}
prod_pts = set_2$points$Role$ProductDesigner 
eng_pts = set_2$points$Role$Engineer
serv_pts = set_2$points$Role$ServiceDesigner

prod_mean_net = set_2$line.weights %>% dplyr::filter(Role == "ProductDesigner") %>% colMeans()
eng_mean_net = set_2$line.weights %>% dplyr::filter(Role == "Engineer") %>% colMeans()
serv_mean_net = set_2$line.weights %>% dplyr::filter(Role == "ServiceDesigner") %>% colMeans()

plot(set_2, title = "Product Designer vs Engineer") |>
  units(
    points = prod_pts, 
    points_color = "red",
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
  units(
    points = eng_pts, 
    points_color = "blue",
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
  edges(
    weights = prod_mean_net - eng_mean_net, # optional multiplier to adjust for readability
    edge_size_multiplier = edge_size_multiplier,
    edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier,
    node_position_multiplier = node_position_multiplier,
    edge_color = c("red","blue")) |>
  nodes(
    node_size_multiplier = node_size_multiplier,
    node_position_multiplier = node_position_multiplier,
    self_connection_color = c("red","blue"))

plot(set_2, title = "Product Designer vs ServiceDesigner") |>
  units(
    points = prod_pts, 
    points_color = "red",
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
  units(
    points =serv_pts, 
    points_color = "green",
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
  edges(
    weights = prod_mean_net - serv_mean_net, # optional multiplier to adjust for readability
    edge_size_multiplier = edge_size_multiplier,
    edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier,
    node_position_multiplier = node_position_multiplier,
    edge_color = c("red","green")) |>
  nodes(
    node_size_multiplier = node_size_multiplier,
    node_position_multiplier = node_position_multiplier,
    self_connection_color = c("red","green"))

plot(set_2, title = "Service Designer vs Engineer") |>
  units(
    points = serv_pts, 
    points_color = "green",
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
  units(
    points = eng_pts, 
    points_color = "blue",
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
  edges(
    weights = serv_mean_net - eng_mean_net, # optional multiplier to adjust for readability
    edge_size_multiplier = 1,
    edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier,
    node_position_multiplier = node_position_multiplier,
    edge_color = c("green","blue")) |>
  nodes(
    node_size_multiplier = node_size_multiplier,
    node_position_multiplier = node_position_multiplier,
    self_connection_color = c("green","blue"))
```

Plot 2: All Means
```{r}

#get list of time phases and groups loop over or use map function

phases = unique(set_2$points$TimePhase)

groups = unique(set_2$points$Role)


col_list_2 = c("red",
              "blue",
              "green")

traces = c(2:10)

x_agency = plot(set_2, title = "Group Means by Phase -- Agency")
count = 1

for (i in 1:length(phases)){
  for (j in 1:length(groups)){
    points = set_2$points %>% filter(TimePhase == phases[i], Role == groups[j])
    #print(head(points))
    x_agency = x_agency |>
      units(
        points = points,
        point_position_multiplier = point_position_multiplier,
        points_color = col_list_2[i],
        show_mean = TRUE, show_points = F, with_ci = FALSE
        ) |>
      nodes(node_size_multiplier = 0.3,
            node_position_multiplier = node_position_multiplier,
            self_connection_color = c("black"))|>
      plotly::layout(showlegend = TRUE, legend = list(x = 100, y = 0.9)) |>
      plotly::style(name = paste0(phases[i]," - ",groups[j]), traces = traces[count])
    count = count + 1
    
  }
}

x_agency
```

Check nesting

```{r}
reg_dat_agency = set_2$points %>% filter(ENA_DIRECTION == "response")

ICC::ICCest(Speaker,SVD1,reg_dat_agency) #not significant

ICC::ICCest(Speaker,SVD2,reg_dat_agency) #significant we will need to include a variable for individual in the model
```


```{r}
mod_x_agency = lm(SVD1 ~ as.factor(TimePhase) + Role, data = reg_dat_agency)
mod_y_agency = lm(SVD2 ~ as.factor(TimePhase) + Role, data = reg_dat_agency)


summary(mod_x_agency)
summary(mod_y_agency)
```

check for interactions: (interactions are significant so we should use those models)
```{r}
mod_x_agency_2 = lm(SVD1 ~ as.factor(TimePhase) + Role + as.factor(TimePhase)*Role, data = reg_dat_agency)
mod_y_agency_2 = lm(SVD2 ~ as.factor(TimePhase) + Role + as.factor(TimePhase)*Role, data = reg_dat_agency)

summary(mod_x_agency_2)
summary(mod_y_agency_2)

anova(mod_x_agency,mod_x_agency_2)
anova(mod_y_agency,mod_y_agency_2)

```

#Need to run mixed model for Y
##model is singular so stick with OLS

```{r}
library(lmerTest)

#mod_y_agency_mixed = lmerTest::lmer(SVD2 ~ 1 + (1|Speaker) + as.factor(TimePhase)*Role ,data = reg_dat_agency)

#summary(mod_y_agency_mixed)
```


Marginal means x - RQ1
```{r}
emm_ag1 = emmeans(mod_x_agency_2, specs = pairwise ~ Role, weights = "proportional")
print(emm_ag1$emmeans)
print(emm_ag1$contrasts)
```

Viewing interactions
```{r}
emmip(mod_x_agency_2, Role ~ TimePhase)

```


Marginal means - x RQ2
```{r}
emm_ag1 = emmeans(mod_x_agency_2, specs = pairwise ~ TimePhase|Role, weights = "proportional")
emm_ag1 = as_tibble(emm_ag1$contrasts)

emm_ag2 = emmeans(mod_x_agency_2, specs = pairwise ~ Role|TimePhase, weights = "proportional")
emm_ag2 = as_tibble(emm_ag2$contrasts)

emm_ag1 = emm_ag1 %>% filter(p.value < 0.05)
emm_ag2 = emm_ag2 %>% filter(p.value < 0.05)
                             
emm_ag1
emm_ag2

```

Effect sizes
```{r}
#todo
```


Marginal means y - RQ1
```{r}
emm_ag_y1 = emmeans(mod_y_agency_2, specs = pairwise ~ Role, weights = "proportional")

print(emm_ag_y1$contrasts)
```

Viewing interactions
```{r}
emmip(mod_y_agency_2, Role ~ TimePhase)
```

Marginal means - y RQ2
```{r}
emm_ag_y1 = emmeans(mod_y_agency_2, specs = pairwise ~ TimePhase|Role, weights = "proportional")
emm_ag_y1 = as_tibble(emm_ag_y1$contrasts)

emm_ag_y2 = emmeans(mod_y_agency_2, specs = pairwise ~ Role|TimePhase, weights = "proportional")
emm_ag_y2 = as_tibble(emm_ag_y2$contrasts)

emm_ag_y1 = emm_ag_y1 %>% filter(p.value < 0.05)
emm_ag_y2 = emm_ag_y2 %>% filter(p.value < 0.05)

emm_ag_y1
emm_ag_y2
```

Calculate eff sizes
```{r}
#to do
```


Model diagnostics
```{r}
check_model(mod_x_agency_2)
check_model(mod_y_agency_2)
```
Looks ok

Plot network subtractions
```{r}
mean1 = set_2$points %>% dplyr::filter(TimePhase == 1, Role == "Engineer")
mean2 = set_2$points %>% dplyr::filter(TimePhase == 1, Role == "ProductDesigner")

mean1_net = set_2$line.weights %>% dplyr::filter(TimePhase == 1, Role == "Engineer") %>% colMeans()
mean2_net = set_2$line.weights %>% dplyr::filter(TimePhase == 1, Role == "ProductDesigner") %>% colMeans()

plot(set_2, title = "Network subtraction") |>
  units(
    points = mean1, 
    points_color = "red",
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
  units(
    points = mean2, 
    points_color = "blue",
    show_mean = TRUE, show_points = FALSE, with_ci = TRUE) |>
  edges(
    weights = mean1_net - mean2_net, # optional multiplier to adjust for readability
    edge_size_multiplier = edge_size_multiplier,
    edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier,
    node_position_multiplier = node_position_multiplier,
    edge_color = c("red","blue")) |>
  nodes(
    node_size_multiplier = node_size_multiplier,
    node_position_multiplier = node_position_multiplier,
    self_connection_color = c("red","blue"))
```


