---
title: "JLA0-2023-ENA"
author: "Zach & Yuanru"
date: "2023-05-23"
output:
  html_document:
    toc: yes
    df_print: paged
  html_notebook:
    toc: yes
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list = ls())
```


```{r include=FALSE}
library(rENA)
library(magrittr)
library(tidyverse)
```

most recent data Ayano shared
```{r}
data <- read.csv("~/Rprojects/ayano/PES_010v6(selected).csv")
#colnames(data)
#time phase is tSSNA
```

```{r}
units <- c("Speaker", "Role", "Phase")

codes_1 <- c("Functions", "Aesthetics", "User", "Vision", "Prototyping") # design actions codes
codes_2 <- c("CA", "ALoK", "CSU", "GCA", "Projective","Regulative","Relational") # shared epistemic agency codes

conversations = c("Role","Phase")

# hoo_rules <- conversation_rules(
#   (TimePhase %in% UNIT$TimePhase & Role %in% UNIT$Role)
# )
```

notes: accum_1 and set_1 are for design action codes; accum_2 and set_2 are for shared epistemic agency codes

```{r}
accum_1 = ena.accumulate.data(units = data[,units],
                              conversation = data[,conversations],
                              codes = data[,codes_1],
                              window.size.back = 4)
```


Note: Not doing means rotation so I can compare everything in the same space

```{r}
set_1 = ena.make.set(accum_1)
```


```{r}
accum_2 = ena.accumulate.data(units = data[,units],
                              conversation = data[,conversations],
                              codes = data[,codes_2],
                              window.size.back = 4)
```

```{r}
set_2 = ena.make.set(accum_2)
```


Model 1: design action codes

Plot 1: Mean Network

```{r}

plot = ena.plot(set_1, scale.to = "points", title = "Groups and Means")  %>%
       ena.plot.points(points = as.matrix(set_1$points)) %>% 
       ena.plot.group(point = as.matrix(set_1$points),
                      colors = c("black"), confidence.interval = "box") %>% 
      ena.plot.network(network = colMeans(as.matrix(set_1$line.weights)),colors = "black")
plot$plot

```

Plot 2: All Means
```{r}

#get list of time phases and groups loop over or use map function

phases = unique(set_1$points$Phase)

groups = unique(set_1$points$Role)

# col_list = list(pd = list("darkolivegreen2","darkolivegreen3","darkolivegreen4"),
#                 en = list("darkorange2","darkorange3","darkorange4"),
#                 sd = list("darkorchid1","darkorchid2","darkorchid3"))

col_list_2 = c("red",
              "blue",
              "green")


x = ena.plot(set_1, title = "Group Means by Phase")

for (i in 1:length(phases)){
  for (j in 1:length(groups)){
    points = set_1$points %>% filter(Phase == phases[i], Role == groups[j]) %>% as.matrix()
    x = x %>% 
      ena.plot.group(points = points,
                     colors = col_list_2[i],
                     confidence.interval = "none",
                     labels = paste(phases[i],groups[j]))
  }
}

x = x %>% ena.plot.network(network = colMeans(as.matrix(set_1$line.weights))*0,colors = "black")
x

```


Stats:

```{r}
reg_dat_design = set_1$points

mod_x_design = lm(SVD1 ~ as.factor(Phase) + Role, data = reg_dat_design)
mod_y_design = lm(SVD2 ~ as.factor(Phase) + Role, data = reg_dat_design)


summary(mod_x_design)
summary(mod_y_design)

```

Marginal means - x

```{r}
library(emmeans)

emm_x_design = emmeans(mod_x_design, specs = pairwise ~ Role|Phase, weights = "proportional")
emm_x_design = emmeans(mod_x_design, specs = pairwise ~ Phase|Role, weights = "proportional")
emm_x_design$contrasts

```

Marginal means - y
```{r}
emm_y_design1 = emmeans(mod_y_design, specs = pairwise ~ Role|Phase, weights = "proportional")
emm_y_design2 = emmeans(mod_y_design, specs = pairwise ~ Phase|Role, weights = "proportional")
emm_y_design1$contrasts
emm_y_design2$contrasts
```

Calculate eff sizes
```{r}

```

Plot network subtractions for moderate to high eff sizes
```{r}
mean1 = set_1$points %>% dplyr::filter(Phase == 1, Role == "Engineer")
mean2 = set_1$points %>% dplyr::filter(Phase == 1, Role == "ProductDesigner")

lw_1 = set_1$line.weights %>% dplyr::filter(Phase == 1, Role == "Engineer") %>% as.matrix() %>% colMeans()
lw_2 = set_1$line.weights %>% dplyr::filter(Phase == 1, Role == "ProductDesigner") %>% as.matrix() %>% colMeans()


plot = ena.plot(set_1, title = "Network Subtractions") %>% 
          ena.plot.points(points = mean1, colors = c("blue")) %>% 
          ena.plot.points(points = mean2, colors = c("red")) %>% 
          ena.plot.group(point = mean1, colors =c("blue"), 
                         confidence.interval = "box") %>% 
          ena.plot.group(point = mean2, colors =c("red"), 
                         confidence.interval = "box") %>%
          ena.plot.network(network = lw_1 - lw_2, colors = c("blue","red"))

plot$plot

```

Model 2: Epistemic Agency Codes

Plot 1: Mean Network

```{r}
plot = ena.plot(set_2, scale.to = "points", title = "Groups and Means")  %>%
       ena.plot.points(points = as.matrix(set_2$points)) %>% 
       ena.plot.group(point = as.matrix(set_2$points),
                      colors = c("black"), confidence.interval = "box") %>% 
      ena.plot.network(network = colMeans(as.matrix(set_2$line.weights)),colors = "black")
plot$plot

```

Plot 2: All Means
```{r}

phases = unique(set_2$points$Phase)

groups = unique(set_2$points$Role)

# col_list = list(pd = list("darkolivegreen2","darkolivegreen3","darkolivegreen4"),
#                 en = list("darkorange2","darkorange3","darkorange4"),
#                 sd = list("darkorchid1","darkorchid2","darkorchid3"))

col_list_2 = c("red",
              "blue",
              "green")


x = ena.plot(set_2, title = "Group Means by Phase")

for (i in 1:length(phases)){
  for (j in 1:length(groups)){
    points = set_2$points %>% filter(Phase == phases[i], Role == groups[j]) %>% as.matrix()
    x = x %>% 
      ena.plot.group(points = points,
                     colors = col_list_2[i],
                     confidence.interval = "none",
                     labels = paste(phases[i],groups[j]))
  }
}

x = x %>% ena.plot.network(network = colMeans(as.matrix(set_2$line.weights))*0,colors = "black")
x
```

```{r}
reg_dat_agency = set_2$points

mod_x_agency = lm(SVD1 ~ as.factor(Phase) + Role, data = reg_dat_agency)
mod_y_agency = lm(SVD2 ~ as.factor(Phase) + Role, data = reg_dat_agency)


summary(mod_x_agency)
summary(mod_y_agency)
```
Marginal means - x

```{r}
emm_x_agency1 = emmeans(mod_x_agency, specs = pairwise ~ Role|Phase, weights = "proportional")
emm_x_agency2 = emmeans(mod_x_agency, specs = pairwise ~ Phase|Role, weights = "proportional")
emm_x_agency1$contrasts
emm_x_agency2$contrasts

```

Marginal means - y
```{r}
emm_y_agency1 = emmeans(mod_y_agency, specs = pairwise ~ Role|Phase, weights = "proportional")
emm_y_agency2 = emmeans(mod_y_agency, specs = pairwise ~ Phase|Role, weights = "proportional")
emm_y_agency1$contrasts
emm_y_agency2$contrasts
```

Calculate eff sizes
```{r}

```

Plot network subtractions for moderate to high eff sizes
```{r}
mean1 = set_1$points %>% dplyr::filter(Phase == 1, Role == "Engineer")
mean2 = set_1$points %>% dplyr::filter(Phase == 1, Role == "ProductDesigner")

lw_1 = set_1$line.weights %>% dplyr::filter(Phase == 1, Role == "Engineer") %>% as.matrix() %>% colMeans()
lw_2 = set_1$line.weights %>% dplyr::filter(Phase == 1, Role == "ProductDesigner") %>% as.matrix() %>% colMeans()


plot = ena.plot(set_1, title = "Network Subtractions") %>% 
          ena.plot.points(points = mean1, colors = c("blue")) %>% 
          ena.plot.points(points = mean2, colors = c("red")) %>% 
          ena.plot.group(point = mean1, colors =c("blue"), 
                         confidence.interval = "box") %>% 
          ena.plot.group(point = mean2, colors =c("red"), 
                         confidence.interval = "box") %>%
          ena.plot.network(network = lw_1 - lw_2, colors = c("blue","red"))

plot$plot
```


