---
title: "Ordered network analysis tutorial"
author: Yuanru Tan
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
your rmarkdown file:
  always_allow_html: yes
---

This tutorial demonstrates how to conduct an Ordered Network Analysis using the `ona` R package. If you are new to ONA as an analytic technique, Tan et al. (2022) provides a more detailed explication of its theoretical and methodological foundations.

Because ONA shares some conceptual and procedural similarities with Epistemic Network Analysis (ENA), you may also want to read the [ENA tutorial paper](https://learning-analytics.info/index.php/JLA/article/view/4329), [ENA example paper](https://www.solaresearch.org/publications/hla-17/hla17-chapter15/), and [ENA mathematical foundation paper](https://link-springer-com.ezproxy.library.wisc.edu/chapter/10.1007/978-3-030-67788-6_7) to familiarize yourself with the theoretical and methodological foundations of ENA.

For a better reading experience, I suggest you use `visual mode` instead of `source mode` to read and use this rmd file. Switch mode by clicking on the Source or Visual on the left top corner.

Due to the practical focus of this tutorial, I omitted detailed explanations of the theoretical, methodological, and mathematical foundations of ONA that are crucial for informed, theory-based learning analytics research. Please reach out to Yuanru Tan (yuanru.tan\@wisc.edu) with any questions! Also, welcome and appreciate any feedback that you might have to make this tutorial more helpful.

# 1. Install the ONA package and load the library

Note: when installing ona or tma package, if you are a Mac user and you run into "package has non-zero exit status" after replying "Yes" to the question "do you want to attempt to install these from sources? (Yes/no/cancel)", please follow this link to install the gfortran that matches the version of your MacOS: <https://github.com/fxcoudert/gfortran-for-macOS/releases>. After you finish the gfortran process, restart your R studio before you install the packages again.

Install the ona package and load the ona library after installing.

```{r message = FALSEinstall.packages("~/Downloads/ona_0.1.1.tar.gz", repos = NULL, type = "source")
```

```{r message = FALSE}
library(ona)
```

Then, install the other package that is required for ONA analysis.

```{r message = FALSE}
install.packages("~/Downloads/tma_0.1.2.tar.gz", repos = NULL, type = "source")
```

```{r message = FALSE}
library(tma )
```

# 2. Dataset

The dataset we will use as an example, `RS.data`, is included in the `ONA` package. Note that the `RS.data` file in the package is only a subset of the full dataset, and is thus intended for demonstration purposes only.

To start, pass `RS.data` from the ONA package to a data frame named **data**.

```{r}
data = ona::RS.data
```

Use the head() function in R to subset and preview the first six rows present in the input data frame to familiarize yourself with the data structure.

```{r}
head(data)
```

`RS.data` consists of discourse from *RescuShell*, an online learning simulation where students work as interns at a fictitious company to solve a realistic engineering design problem in a simulated work environment. Throughout the internship, students communicate with their project teams and mentors via online chat, and these chats are recorded in the "text" column. A set of qualitative codes were applied to the data in the "text" column, where a value of 0 indicates the absence of the code and a value of 1 indicates the presence of the code in a given line.

# 3. Construct an ONA model

To construct an ONA model, identify which columns in the data to use for the parameters required by the ONA modeling function.

## 3.1 Specify units

In ONA, *units* can be individuals, ideas, organizations, or any other entity whose structure of connections you want to model. To set the units parameter, specify which column(s) in the data contain the variables that identify unique units.

For this example, choose the "Condition" column and the "UserName" column to define the units. The "Condition" column has two unique values: FirstGame, and SecondGame, representing novice users and relative expert users, respectively, as some students participated in *RescuShell* after having already completed a different engineering virtual internship. The "UserName" column includes unique user names for all students (*n*=48). This way of defining the units means that ONA will construct a network for each student in each condition.

```{r}
my_units <- c("Condition", "UserName") 
```

## 3.2 Specify codes

Next, specify the columns that contain the *codes*. Codes are concepts whose pattern of association you want to model for each unit. ONA represent codes as nodes in the networks and co-occurrences of codes as edges. Most researchers use binary coding in ONA analyses, where the values in the code columns are either 0 (indicating that the code is not present in that line) or 1 (indicating that the code is present in that line). `RS.data` contains six code columns, all of which will be used here.

```{r}
my_codes = c(
          'Data',
          'Technical.Constraints',
          'Performance.Parameters',
          'Client.and.Consultant.Requests',
          'Design.Reasoning',
          'Collaboration')
```

## 3.3 Specify conversations

The parameter to specify *conversations* in ONA is called "my_hoo_rules", where "hoo" is an abbreviation of "horizon of observation."

The conversation parameter determines which lines in the data *can* be connected. Codes in lines that are not in the same conversation cannot be connected. For example, you may want to model connections within different time segments, such as days, or different steps in a process, such as activities.

In our example, choose the "Condition", "GroupName", and "ActivityNumber" columns to define the conversations. These choices indicate that connections can only happen between students who were in the same condition (FirstGame or SecondGame) and on the same project team (group), and within the same activity. This definition of conversation reflects what actually happened in the simulation: in a given condition, students only interacted with those who were in the same group, and each activity occurred on a different day.

Choose the combination of "Condition" column, "GroupName" column, and "ActivityNumber" column to define the conversation parameter.

```{r}
my_hoo_rules <- conversation_rules(
                  (Condition %in% UNIT$Condition & 
                   GroupName %in% UNIT$GroupName & 
                   ActivityNumber %in% UNIT$ActivityNumber))
```

## 3.4 Specify the window

Once the conversation parameter is specified, a window method needs to be specified. Whereas the conversation parameter specifies which lines *can be* related, the window parameter determines which lines within the same conversation *are* related. The most common window method used in ONA is called a moving stanza window, which is what will be used here.

Briefly, a moving stanza window is a sliding window of fixed length that moves through a conversation to detect and accumulate code co-occurrences in recent temporal context. The lines within a designated stanza window are considered related to each other. For instance, if the moving stanza window is 7, then each line in the conversation is linked to the six preceding lines. See [Siebert-Evenstone et al. (2017)](https://learning-analytics.info/index.php/JLA/article/view/5416) and [Ruis et al. (2019)](https://repository.isls.org/handle/1/770) for more detailed explanations of windows.

Specify a moving stanza window size by passing a numerical value to the `window_size` parameter.

```{r}
window_size = 7
```

To specify an infinite stanza window in ONA, set the size of the moving window equal to or larger than the number of lines in the longest conversation. For example, set `window_size = 4000`, which is greater than the total number of rows in our dataset (nrows=3,824). The infinite stanza window works the same way as a moving stanza window, but there is no limit on the number of previous lines that are included in the window besides the conversation itself.

## 3.5 Specify metadata

Metadata columns can be included if desired. Metadata columns are not required to construct an ONA model, but they provide information that can be used to subset units in the resulting model.

```{r}
metaCols = c("CONFIDENCE.Change","CONFIDENCE.Pre","CONFIDENCE.Post","C.Change")
```

## 3.6 Accumulate connections

Now that all the parameters are specified, connections can be accumulated. For each unit, the ONA algorithm uses a moving stanza window to identify connections formed from a current line of data (e.g., a turn of talk), or *response*, to the preceding lines within the window (the *common ground*).

Unlike in unordered model such as ENA, where connections among codes are recorded in a symmetric adjacency matrix, ONA accounts for the order in which the connections occur by constructing an *asymmetric adjacency matrix* for each unit; that is, the number of connections from code A to code B may be different than the number of connections from B to A.

To accumulate connections, pass the parameters specified to the `contexts` and `accumulate_contexts` functions, and store the output in an object (in this case, **accum.ona**).

```{r}
accum.ona <-
  contexts(data, 
           units_by = my_units, 
           hoo_rules = my_hoo_rules) |>
  accumulate_contexts(codes = my_codes, 
                      decay.function = decay(simple_window, window_size = 7),
                      meta.data = metaCols,
                      return.ena.set = FALSE) # keep this as FALSE to get an ONA model, otherwise it will return an undirected model)
```

## 3.7 Construct an ONA model

After accumulation, call the `model` function to construct an ONA model. ONA currently implements *singular value decomposition* (SVD) and *means rotation* (MR) to perform dimensional reduction.

To create an ONA model using SVD, pass the `accum.ona` object to the `model` function.

```{r}
set.ona <- 
  model(accum.ona)
```

When there are two discrete groups to compare, a means rotation can be used.

A means rotation is specified using `rotate.using ="mean"` in the `model` function. Additionally, the `model` function expects `rotation.params` to be a `list` with two named elements, each containing a logical vector representing the rows of units to be included in each group.

Here, construct the ONA model as shown below.

```{r}
set.ona <-
  model(accum.ona,                             # the previously run accumulation above
        rotate.using ="mean",                  # means rotation method
        rotation.params =                      # two groups for means rotation in a list
              list(FirstGame=accum.ona$meta.data$Condition=="FirstGame",
                   SecondGame=accum.ona$meta.data$Condition=="SecondGame")   
        )
```

# 4. Summary of key model outputs

Information about an ONA model is now stored in the R object `set.ona`. Users can explore the data stored in the object by typing `set.ona$` and select items from the drop down list. Here, we briefly explain the top-level items in `set.ona$`.

## 4.1 Connection counts

Because ONA accounts for the order in which the connections occur by constructing an *asymmetric adjacency matrix* for each unit, connection counts *from* code A *to* code B and *from* B *to* A, as well as self-connections for each code (from A to A) are recorded. Thus, because six codes were included in the model, the cumulative adjacency vector for each unit contains 36 terms (*n*\^2).

```{r}
head(set.ona$connection.counts,3)
```

## 4.2 Line weights

In `set.ona$connection.counts`, the value for each unique co-occurrence of codes is an integer equal or greater than 0, because they represent the directional connection counts between each pair of codes. In `set.ona$line.weights`, the connection counts are sphere normalized, and so the values are between 0 and 1.

```{r}
head(set.ona$line.weights,3)
```

## 4.3 ONA points

For each unit, ONA produces an ONA point in a two-dimensional space formed by the first two dimensions of the dimensional reduction.

Here, the MR1 column represents the *x*-axis coordinate for each unit, and the SVD2 column represents the *y*-axis coordinate for each unit.

```{r}
head(set.ona$points,3)
```

## 4.4 Rotation matrix

The rotation matrix used during the dimensional reduction can be accessed through `set.ona$rotation`. This is mostly useful when you want to construct an ONA metric space using one dataset and then project ONA points from different data into that space, as in section 8.1.

```{r}
head(set.ona$rotation.matrix,3)
```

## 4.5 Metadata

`set.ona$meta.data` gives a data frame that includes all the columns except for the code connection columns.

```{r}
head(set.ona$meta.data,3)
```

# 5. ONA visualization

Once an ONA model is constructed, ONA networks can be visualize. The plotting function in ONA is called `plot`.

Before plotting, you can set up several global parameters to ensure consistency across plots. These parameters will be clearer in subsequent sections.

```{r}
node_size_multiplier = 0.4 # scale up or down node sizes
node_position_multiplier = 1 # zoom in or out node positions
point_position_multiplier = 1.5 # zoom in or out the point positions
edge_arrow_saturation_multiplier = 1.5 # adjust the chevron color lighter or darker
edge_size_multiplier = 1 # scale up or down edge sizes
```

## 5.1 Plot a mean network and its points

Mean ONA networks can be plotted for each of the conditions along with their subtracted network.

First, plot the mean network for the FirstGame condition. Use a pipe `|>` to connect the `edges` function and the `nodes` function. Users are only required to specify the `weights` parameter, as the remaining parameters have default values unless specified otherwise.

Use `set.ona$points` to subset the rows that are in each condition and plot the units in each condition as a different color.

The points are specified in the `units` function. The `edges` and `nodes` functions remain the same as above.

```{r}
plot(set.ona, title = "FirstGame (red) mean network") |>
  units(
    points=set.ona$points$Condition$FirstGame, 
    point_position_multiplier = point_position_multiplier,
    points_color = c("red"),
    show_mean = TRUE, show_points = TRUE, with_ci = TRUE) |>
  edges(
    weights =set.ona$line.weights$Condition$FirstGame,
    edge_size_multiplier = edge_size_multiplier,
    edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier,
    node_position_multiplier = node_position_multiplier,
    edge_color = c("red")) |>
  nodes(
    node_size_multiplier = node_size_multiplier,
    node_position_multiplier = node_position_multiplier,
    node_labels = TRUE, # change this to FALSE can remove node labels in case you want to add them back in a nicer font or size for your presentations or publications
    self_connection_color = c("red"))

```

Since this is the first ONA network visualization in this chapter, we briefly explain how to read an ONA network.

**Node size**: In ONA, the node size is proportional to the number of occurrences of that code as a *response* to other codes in the data, with larger nodes indicating more responses. For example, in this plot, students in the FirstGame condition responded most frequently with discourse about Technical.Constraints.

**Self-connections**: The color and saturation of the circle within each node is proportional to the number of *self-connections* for that code: that is, when a code is both what students *responded to* and what they *responded with.* Colored circles that are larger and more saturated reflect codes with more frequent self-connections.

**Edges**: Note that unlike most directed network visualizations, which use arrows or spearheads to indicate direction, ONA uses a "broadcast" model, where the source of a connection (what students responded to) is placed at the apex side of the triangle and the destination of a connection (what students responded with) is placed at its base.

**Chevrons on edges**: The chevrons point in the direction of the connection. Between any pair of nodes, if there is a bidirectional connection, the chevron only appears on the side with the stronger connection. This helps viewers differentiate heavier edges in cases such as between Technical.Constraints and Data, where the connection strengths from both directions are similar. When the connection strengths are identical between two codes, the chevron will appear on both edges.

```{r}
plot(set.ona, title = "SecondGame (blue) mean network") |>
  units(
    points=set.ona$points$Condition$SecondGame, 
    points_color = "blue", 
    show_mean = TRUE, show_points = TRUE, with_ci = TRUE) |>
  edges(
    weights = set.ona$line.weights$Condition$SecondGame,
    edge_size_multiplier = edge_size_multiplier,
    edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier,
    node_position_multiplier = node_position_multiplier,
    edge_color = c("blue")) |>
  nodes(
    node_size_multiplier = node_size_multiplier,
    node_position_multiplier = node_position_multiplier,
    self_connection_color = c("blue"))

```

Plot the subtracted network as follows.

```{r}
# FirstGame and SecondGame subtracted plot
plot(set.ona, title = "Difference: FirstGame (red) vs SecondGame (blue)") |>
  units(
    points = set.ona$points$Condition$FirstGame, 
    points_color = "red",
    show_mean = TRUE, show_points = TRUE, with_ci = TRUE) |>
  units(
    points = set.ona$points$Condition$SecondGame, 
    points_color = "blue",
    show_mean = TRUE, show_points = TRUE, with_ci = TRUE) |>
  edges(
    weights = (colMeans(set.ona$line.weights$Condition$FirstGame) - colMeans(set.ona$line.weights$Condition$SecondGame))*4, # optional multiplier to adjust for readability
    edge_size_multiplier = edge_size_multiplier,
    edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier,
    node_position_multiplier = node_position_multiplier,
    edge_color = c("red","blue")) |>
  nodes(
    node_size_multiplier = node_size_multiplier,
    node_position_multiplier = node_position_multiplier,
    self_connection_color = c("red","blue"))
```

## 5.2 Plot an individual network and its points

To plot an individual student's network and ONA point, use `set.ona$points`.

```{r compare two individual units}
# first game
plot(set.ona, title = "FirstGame::steven z") |>
  units(
    points=set.ona$points$ENA_UNIT$`FirstGame::steven z`, 
    points_color = "red", 
    show_mean = FALSE, show_points = TRUE, with_ci = FALSE) |>
  edges(
    weights = set.ona$line.weights$ENA_UNIT$`FirstGame::steven z`,
    edge_size_multiplier = edge_size_multiplier,
    edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier,
    node_position_multiplier = node_position_multiplier,
    edge_color = c("red")) |>
  nodes(
    node_size_multiplier = node_size_multiplier,
    node_position_multiplier = node_position_multiplier,
    self_connection_color = c("red"))

# second game
plot(set.ona, title = "SecondGame::samuel o") |>
  units(
    points=set.ona$points$ENA_UNIT$`SecondGame::samuel o`, 
    points_color = "blue", 
    show_mean = FALSE, show_points = TRUE, with_ci = FALSE) |>
  edges(
    weights = set.ona$line.weights$ENA_UNIT$`SecondGame::samuel o`,
    edge_size_multiplier = edge_size_multiplier,
    edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier,
    node_position_multiplier = node_position_multiplier,
    edge_color = c("blue")) |>
  nodes(
    node_size_multiplier = node_size_multiplier,
    node_position_multiplier = node_position_multiplier,
    self_connection_color = c("blue"))
```

In this case, both units make relatively strong connections between Design.Reasoning and Data. However, for Unit A (red), the connection is relatively more *from* Design.Reasoning *to* Data than the other way around. This indicates that more often this unit responded with Data. In contrast, Unit B (blue) responded more frequently to Data with Design.Reasoning.

A subtracted network can make such differences more salient.

```{r}
# units difference
mean1 = as.vector(as.matrix(set.ona$line.weights$ENA_UNIT$`FirstGame::steven z`))
mean2 = as.vector(as.matrix(set.ona$line.weights$ENA_UNIT$`SecondGame::samuel o`))

subtracted.mean = mean1 - mean2

plot(set.ona, title = "subtracted network of steven z (red) and Samuel (blue)") |> 
  units(
    points = set.ona$points$ENA_UNIT$`FirstGame::steven z`, points_color = "red",
    point_position_multiplier = point_position_multiplier,
    show_mean = FALSE, show_points = TRUE, with_ci = FALSE) |>
  units(
    points = set.ona$points$ENA_UNIT$`SecondGame::samuel o`, points_color = "blue",
    point_position_multiplier = point_position_multiplier,
    show_mean = FALSE, show_points = TRUE, with_ci = FALSE) |>
  edges(
    weights = subtracted.mean*2,
    edge_size_multiplier = edge_size_multiplier,
    edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier,
    node_position_multiplier = node_position_multiplier,
    edge_color = c("red", "blue")) |>
  nodes(
    node_size_multiplier = node_size_multiplier,
    node_position_multiplier = node_position_multiplier,
    self_connection_color = c("red", "blue")) 
```

The connection between Design.Reasoning and Data consists of two triangles, one in blue pointing from Data to Design.Reasoning, the other in red pointing from Design.Reasoning to Data. This indicates that although both units made strong connections between these two codes, the relative directed frequencies are different. Recall that in the ENA subtracted network for the same two units, the connections between Data and Design.Reasoning were basically the same. ONA, by accounting for the order of events, shows that while the undirected relative frequencies were similar, there was a difference in the order in which the two students made the connection.

# 6. Compare groups statistically

In addition to visual comparison of networks, ENA points can be analyzed statistically. For example, here we might test whether the patterns of association in one condition are significantly different from those in the other condition.

To demonstrate both parametric and non-parametric approaches to this question, the examples below use a Student's *t* test and a Mann-Whitney *U* test to test for differences between the FirstGame and SecondGame condition.

First, install the `lsr` package to enable calculation of effect size (Cohen's *d*) for the *t* test.

```{r}
install.packages('lsr')
library(lsr)
```

Then, subset the points to test for differences between the points of the two conditions.

```{r}
ona_first_points_d1 = as.matrix(set.ona$points$Condition$FirstGame)[,1]
ona_second_points_d1 = as.matrix(set.ona$points$Condition$SecondGame)[,1]

ona_first_points_d2 = as.matrix(set.ona$points$Condition$FirstGame)[,2]
ona_second_points_d2 = as.matrix(set.ona$points$Condition$SecondGame)[,2]
```

Conduct the *t* test on the first and second dimensions.

```{r}
# parametric tests
t_test_d1 = t.test(ona_first_points_d1, ona_second_points_d1)
t_test_d1

t_test_d2 = t.test(ona_first_points_d2, ona_second_points_d2)
t_test_d2
```

Compute any other statistics that may be of interest. A few examples are given below.

```{r}
mean(ona_first_points_d1)
mean(ona_second_points_d1)
mean(ona_first_points_d2)
mean(ona_second_points_d2)

sd(ona_first_points_d1)
sd(ona_second_points_d1)
sd(ona_first_points_d2)
sd(ona_second_points_d2)

length(ona_first_points_d1)
length(ona_second_points_d1)
length(ona_first_points_d2)
length(ona_second_points_d2)

cohensD(ona_first_points_d1, ona_second_points_d1)
cohensD(ona_first_points_d2, ona_second_points_d2)
```

Here, along the *x* axis (MR1), a two-sample *t* test assuming unequal variance shows that the FirstGame (mean=-0.05, SD=0.09, N=26) condition is statistically significantly different for alpha=0.05 from the SecondGame condition (mean=0.06, SD=0.12, N=22; t(41.001)= -3.77, p=0.00, Cohen's d=1.1). Along the *y* axis (SVD2), a two-sample *t* test assuming unequal variance shows that the FirstGame condition (mean=-1.73, SD=0.17, N=26) is not statistically significantly different for alpha=0.05 from the SecondGame condition (mean=1,74, SD=0.17, N=22; t(45.45)= 0, p=1.00, Cohen's d=0.00).

The Mann-Whitney *U* test is a non-parametric alternative to the independent two-sample *t* test.

First, install the `rcompanion` package to calculate the effect size (*r*) for a Mann-Whitney *U* test.

```{r}
# install.packages('rcompanion')
library(rcompanion)
```

Then, conduct a Mann-Whitney *U* test on the first and second dimensions.

```{r}
# non parametric tests
w_test_d1 = wilcox.test(ona_first_points_d1, ona_second_points_d1)
w_test_d2 = wilcox.test(ona_first_points_d2, ona_second_points_d2)

w_test_d1
w_test_d2
```

Compute any other statistics that may be of interest. A few examples are given below.

```{r}
median(ona_first_points_d1)
median(ona_second_points_d1)
median(ona_first_points_d2)
median(ona_second_points_d2)

length(ona_first_points_d1)
length(ona_second_points_d1)
length(ona_first_points_d2)
length(ona_second_points_d2)

abs(wilcoxonR(ona_first_points_d1, ona_second_points_d1))
abs(wilcoxonR(ona_first_points_d2, ona_second_points_d2))
```

Here, along the *x* axis (MR1), a Mann-Whitney *U* test shows that the FirstGame condition (Mdn=-0.04, N=26) was statistically significantly different for alpha=0.05 from the SecondGame condition (Mdn=0.10, N=22 U=130, p=0.001, r=0.00). Along the *y* axis (SVD2), a Mann-Whitney *U* test shows that the FirstGame condition (Mdn=0.001, N=26) is not statistically significantly different for alpha=0.05 from the SecondGame condition (Mdn=0.00, N=22, U=264, p=0.66, r=0.71). The absolute value of `r` value in Mann-Whitney U test varies from 0 to close to 1. The interpretation values for r commonly in published literature is: `0.10 - < 0.3` (small effect), `0.30 - < 0.5` (moderate effect) and `>= 0.5` (large effect).

# 7 Model evaluation

## 7.1 Variance explained

Briefly, variance explained (also called explained variation) refers to the proportion of the total variance in a dataset that is accounted for by a statistical model or set of predictors.

In ONA, to represent high-dimensional vectors in a two-dimensional space, ONA uses either singular value decomposition or means rotation combined with SVD. For each of the reduced dimensions, the variance in patterns of association among units explained by that dimension can be computed.

```{r}
head(set.ona$model$variance,2)
```

In our example above, since we used means rotation method, the first dimension is labeled as MR1 and the second dimension is labeled as SVD2.The two dimensions in combination explained about 40% of the variance.

As with any statistical model, greater explained variance does not necessarily indicate a better model, as it may be due to overfitting, but it provides one indicator of model quality.

## 7.2 Goodness of fit

Briefly, a model's goodness of fit refers to how well a model fits or represents the data. A model with a high goodness of fit indicates that it accurately represents the data and can make reliable predictions.

In ONA, a good fit means that the positions of the nodes in the space---and thus the network visualizations---are consistent with the mathematical properties of the model. In other words, we can confidently rely on the network visualizations to interpret the ONA model. The process that ONA uses to achieve high goodness of fit is called co-registration, the same as the one used in ENA. The mathematical details of co-registration are beyond the scope of this chapter and can be found in Bowman et al., (2022).

To test a model's goodness of fit, use `ona::correlations`. The closer the value is to 1, the higher the model's goodness of fit is. Most ENA models have a goodness of fit that is well above 0.90.

```{r}
ona::correlations(set.ona)
```

## 7.3 Close the interpretative loop

Another approach to evaluate an ONA model is to confirm the alignment between quantitative model (in our case, our ONA model) and the original qualitative data. In other words, we can return to the original data to confirm that quantitative findings give a fair representation of the data. This approach is an example of what's called as closing the interpretative loop in Quantitative Ethnography field (Shaffer, 2017).

For example, based on our visual analysis of the network of "SecondGame::samuel o" in previous section, we are interested in what the lines are in the original data that contributed to the connection *from* Performance.Parameters *to* Design.Reasoning.

Let's first review what "SecondGame::samuel o" ONA network looks like. Based on the connection direction and strength from Technical.Constraints to Performance.Parameters, we would expect to see more examples of Samuel responded with "Design.Reasoning" to "Performance.Parameters", than the other way around.

```{r}
plot(set.ona, title = "SecondGame::samuel o") |>
  units(
    points=set.ona$points$ENA_UNIT$`SecondGame::samuel o`, 
    points_color = "blue", 
    show_mean = FALSE, show_points = TRUE, with_ci = FALSE) |>
  edges(
    weights = set.ona$line.weights$ENA_UNIT$`SecondGame::samuel o`,
    edge_size_multiplier = edge_size_multiplier,
    edge_arrow_saturation_multiplier = edge_arrow_saturation_multiplier,
    node_position_multiplier = node_position_multiplier,
    edge_color = c("blue")) |>
  nodes(
    node_size_multiplier = node_size_multiplier,
    node_position_multiplier = node_position_multiplier,
    self_connection_color = c("blue"))
```

To do so, we use `view()` function and specify required parameters as below.

This is going to activate a window shows up in your `Viewer` panel. If it is too small to read, you can click on the "Show in new window" button to view it in your browser for better readability.

```{r include=FALSE}
view(accum.ona, # the object stored our connection accmulation reults in 4.3.6
     wh = c("SecondGame::samuel o"), # the unit we are intersted in
     units.by = c("Condition", "UserName"), # consistent with in 4.3.1 
     conversation.by = c("Condition", "GroupName", "ActivityNumber"), # consistent with in 4.3.3
     codes = c("Performance.Parameters", "Design.Reasoning"), # codes of choice
     window = 7) # consistent with in 4.3.4
```

In the `Viewer` panel, hover over your cursor on any of the lines that are in bold, a size of 7 lines rectangle shows up, representing that in a moving stanza window of size 7, the referent line (the line in bold) and its preceding 6 lines. The 1 and 0 in Technical.Constraints column and Design.Reasoning column shows where the connections happened.

Notice that here we are viewing the same qualitative example as in section 3.7.3 in ENA. In line 2477 Samuel shared his [Design.Reasoning] about "mindful of (the) how one device scores relative to other ones", ***as a response to*** what Casey said in line 2476 about [Performance.Parameters] "not one source/censor can be the best in every area so we had to sacrifice certain attributes", as well as what Jackson said in line 2475 about safety as one of the [Performance.Parameters] "when it came to the different attributes, i think that all were important in their own way but i think safety is one of the most important".

Here, ONA was able to not only capture the occurrence between code Design.Reasoning and Performance.Parameters as ENA did, but also represent the connection direction *from* Design.Reasoning *to* Performance.Parameters

# 8. Additional stuff

## 8.1 Projection

To project the ONA points from one model into a space constructed with different data, replace the `rotation.set` parameter of `model`. In the example below, an "expert" model is developed using the SecondGame units and the FirstGame (novice) units are projected into that space.

```{r}
data = ona::RS.data

#expert data
exp.data = subset(data, Condition == "SecondGame")

#novice data
nov.data = subset(data, Condition == "FirstGame")

#shared unit cols  
units = c("UserName","Condition","GroupName") 

#shared code cols
codes = c(
          'Data',
          'Technical.Constraints',
          'Performance.Parameters',
          'Client.and.Consultant.Requests',
          'Design.Reasoning',
          'Collaboration')

#shared hoo
hoo = conversation_rules(
  (Condition %in% UNIT$Condition & GroupName %in% UNIT$GroupName))


#expert accum
accum.exp = contexts(exp.data, units_by = units, hoo_rules = hoo) |>
  accumulate_contexts(codes = codes, 
                      decay.function = decay(simple_window, window_size = 7),
                      return.ena.set = FALSE, norm.by = NULL)
#expert model
set.exp = model(accum.exp)

#novice accum
accum.nov = contexts(nov.data, units_by = units, hoo_rules = hoo) |>
  accumulate_contexts(codes = codes, 
                      decay.function = decay(simple_window, window_size = 7),
                      return.ena.set = FALSE, norm.by = NULL)
#novice model
set.nov = model(accum.nov)

# projecting novice data into expert space
set = model(accum.nov, rotation.set = set.exp$rotation)

plot(set, title = "novice data into expert space") |> 
  units(
    points = set$points, 
    show_mean = TRUE, show_points = TRUE, with_ci = TRUE) |>
  edges(
    weights = set$line.weights) |>
  nodes(
    self_connection_color = "red",
    node_size_multiplier = 0.6) 

```
